Challenges and Solutions of Developing and Implementing a Revolutionary Novel Desktop-as-a-Service

### 2024-04-26 paper.tex
More content (e.g. in subsection 4.4)

Developing the automatic adaptation of the output to the limits of the respective application window is challenging. Only a few VNC and RDP servers make exporting the output of only individual windows or processes possible~\cite{OJCC_2023v8i1n01_Baun}. For Windows operating systems, the proprietary built-in RDP server and the free software TightVNC offer the export of full desktops and single windows. For Linux operating system deployments, the free software projects xrdp and x11vnc enable all desired features (see Table~\ref{tab:DaaS_Services_Overview}).

\begin{table}
	\centering
	\caption{Services used by our DaaS for Remote Access to individual Linux or Windows Applications}
	\begin{tabular}{|l|c|c|c|c|}
		\hline
		\textbf{Service}    &  \textbf{Protocol}  & \textbf{Export of}           & \textbf{Operating} & \textbf{Software}  \\
		\textbf{implementation}  &                & \textbf{single Window only}  & \textbf{System}    & \textbf{License}   \\
		\hline
		TightVNC            &  VNC                & supported                    & Windows            & GPL2               \\
		\hline
		Windows RDP server  &  RDP                & supported                    & Windows            & proprietary        \\
		\hline
		x11vnc              &  VNC                & supported                    & Linux              & GPL2               \\
		\hline
		Xrdp                &  RDP                & supported                    & Linux              & Apache 2.0         \\
		\hline
	\end{tabular}
	\label{tab:DaaS_Services_Overview}
\end{table}

>>>>

Developing the automatic adaptation of the output to the limits of the respective application window is challenging. Only a few RDP and VNC server implementations offer to export the graphical output of only individual windows or processes. For Windows operating systems, the proprietary built-in RDP server and the free software TightVNC offer the export of full desktops and single windows. For Linux operating system deployments, the free software projects xrdp and x11vnc enable all desired features. Table ~\ref{tab:DaaS_Services_Overview} includes an overview of the mentioned service implementations for RDP and VNC protocols and their relevant characteristics. Further implementations like TigerVNC and protocols like NoMachine NX exist but do not seem useful in a novem DaaS design and implementation because they do not meet all feature requirements.~\cite{OJCC_2023v8i1n01_Baun}

\begin{table}
	\centering
	\caption{Services used by our DaaS for Remote Access to individual Linux or Windows Applications}
	\begin{tabular}{|l|c|c|c|c|}
		\hline
		\textbf{Service}    &  \textbf{Protocol}  & \textbf{Single Window}       & \textbf{Operating} & \textbf{Software}  \\
		\textbf{implementation}  &                & \textbf{Mode}                & \textbf{System}    & \textbf{License}   \\
		\hline
		TightVNC            &  VNC                & supported                    & Windows            & GPL2               \\
		\hline
		Windows RDP server  &  RDP                & supported                    & Windows            & proprietary        \\
		\hline
		x11vnc              &  VNC                & supported                    & Linux              & GPL2               \\
		\hline
		Xrdp                &  RDP                & supported                    & Linux              & Apache 2.0         \\
		\hline
	\end{tabular}
	\label{tab:DaaS_Services_Overview}
\end{table}
